---
title: "Advanced Techniques with ggsaveR"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Advanced Techniques with ggsaveR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Introduction

This vignette covers the most advanced features of `ggsaveR`, focusing on reproducibility and fine-grained control. We will explore how to embed reproducibility data into PNG files and how to use the `guard` argument to bypass global settings for specific `ggsave()` calls.

```{r}
library(ggplot2)
library(ggsaveR)
```

## Reproducibility: Embedding Data in PNGs

For maximum reproducibility, `ggsaveR` can embed the `ggplot` object, the R code that generated it, and session information directly into the PNG file's metadata. This is controlled by the `ggsaveR.embed_data` option.

```{r}
options(ggsaveR.embed_data = TRUE)
```

When this option is `TRUE`, any plot saved as a PNG will contain this extra information. `ggsaveR` captures the plot-generating code, even when using pipes.

```{r, eval=FALSE}
# The plot object and the code below are embedded in the PNG file
iris |>
  subset(Species != "setosa") |>
  ggplot(aes(Sepal.Length, Petal.Length)) +
  geom_point(aes(color = Species)) |>
  ggsave("plot_with_embedded_data.png")
```

You can then use the `read_ggsaveR_data()` function to extract this information from the saved PNG.

```{r, eval=FALSE}
# Read the embedded data
embedded_info <- read_ggsaveR_data("plot_with_embedded_data.png")

# View the code that generated the plot
cat(embedded_info$plot_call)
#> iris |>
#>   subset(Species != "setosa") |>
#>   ggplot(aes(Sepal.Length, Petal.Length)) +
#>   geom_point(aes(color = Species))

# You can even replot the original ggplot object
# embedded_info$plot_object
```

```{r}
# Reset the option
options(ggsaveR.embed_data = FALSE)
```

## The Escape Hatch: `guard = TRUE`

Sometimes you have global options set but need to bypass them for a single, specific `ggsave()` call. The `guard = TRUE` argument serves as an "escape hatch," telling `ggsaveR` to step aside and pass the call directly to the original `ggplot2::ggsave`.

### Use Case: Preventing Sensitive Data Embedding

Imagine you have `ggsaveR.embed_data = TRUE` set globally for reproducibility. However, one specific plot is generated from sensitive or very large data that you do not want to embed in the PNG file.

```{r, eval=FALSE}
# Global setting for reproducibility
options(ggsaveR.embed_data = TRUE)

# This plot contains sensitive information
sensitive_data <- data.frame(
  x = rnorm(10),
  y = rnorm(10),
  secret = "Confidential Information"
)
p_sensitive <- ggplot(sensitive_data, aes(x, y)) + geom_point()

# Use guard = TRUE to save the plot without embedding the data
# This call will use the standard ggplot2::ggsave behavior
ggsave("sensitive_plot.png", p_sensitive, guard = TRUE)
```

The `guard = TRUE` argument ensures that for this one call, none of the `ggsaveR` enhancements are applied. The plot will be saved as a standard PNG, without any embedded data, and it will overwrite any existing file with the same name, regardless of the `ggsaveR.overwrite_action` setting.

> **Warning:** Using `guard = TRUE` in a script requires that the `ggsaveR` package is loaded. If it is not, the original `ggplot2::ggsave` will throw an "unused argument" error for `guard`.

These advanced features make `ggsaveR` a powerful tool for managing complex data analysis workflows, enhancing reproducibility while providing the flexibility to handle exceptions.
