---
title: "Getting Started with ggsaveR"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting Started with ggsaveR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Introduction

The `ggsaveR` package is designed to supercharge `ggplot2::ggsave()` without requiring you to change your existing code. This vignette will walk you through the simplest, most common use case: making `ggsave()` better with a single line of code.

## The Problem

Imagine you have an analysis script that saves several plots.

```{r}
library(ggplot2)

# Create a plot
p <- ggplot(mtcars, aes(mpg, wt)) +
  geom_point() +
  labs(title = "Fuel Efficiency vs. Weight")

# Save the plot
# In a real script, you might save this in a 'figures' directory
# ggsave("figures/mpg_vs_wt.png", p)
```

If you want to change how the plot is saved—for example, to add a PDF version for a publication—you would normally have to find and modify every `ggsave()` call.

## The `ggsaveR` Solution

With `ggsaveR`, you can set global options to control the behavior of all subsequent `ggsave()` calls.

First, load the `ggsaveR` library.

```{r}
library(ggsaveR)
```

Now, let's say you want every plot to be saved as both a PNG and a PDF. You can set the `ggsaveR.formats` option at the top of your script.

```{r}
options(ggsaveR.formats = list(
  list(device = "png", dpi = 300),
  list(device = "pdf")
))
```

Now, when you call `ggsave()`, it will automatically save to both formats. The file extension in the `filename` argument is used as the base name.

```{r, eval=FALSE}
# This single call will create both "mpg_vs_wt.png" and "mpg_vs_wt.pdf"
ggsave("mpg_vs_wt.png", p)
```

This simple setup allows you to enhance all plot-saving operations in an existing project by adding just two lines of code to the top of your script.

To clean up, you can reset the option to `NULL`.

```{r}
options(ggsaveR.formats = NULL)
```

This vignette has shown the most basic feature of `ggsaveR`. The other vignettes in this series will explore more advanced capabilities.
