---
title: "Intermediate Usage of ggsaveR"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Intermediate Usage of ggsaveR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Introduction

This vignette builds on the basics covered in "Getting Started with ggsaveR" and explores more advanced features, such as saving plots in multiple dimensions and preventing accidental file overwrites.

```{r}
library(ggplot2)
library(ggsaveR)

# Create a sample plot
p <- ggplot(iris, aes(Sepal.Length, Petal.Length, color = Species)) +
  geom_point() +
  labs(title = "Sepal Length vs. Petal Length")
```

## Saving Multiple Formats and Dimensions

In the previous vignette, we saw how to save a plot in multiple formats. The `ggsaveR.formats` option is highly flexible and allows you to specify different dimensions, resolutions, and other parameters for each file.

Let's define a set of formats for different purposes: a high-resolution PNG for a presentation, a PDF for a manuscript, and an SVG for web use.

```{r}
options(ggsaveR.formats = list(
  # A high-res PNG for presentations
  list(device = "png", width = 8, height = 5, units = "in", dpi = 300),
  # A PDF for a manuscript, with dimensions in centimeters
  list(device = "pdf", width = 18, height = 11, units = "cm"),
  # An SVG for web/editing
  list(device = "svg", width = 7, height = 4.5)
))
```

Now, a single `ggsave()` call will generate all three files with their respective specifications. The original file extension is ignored, and the `filename` is used as a base name.

```{r, eval=FALSE}
# This creates "iris_plot.png", "iris_plot.pdf", and "iris_plot.svg"
ggsave("outputs/iris_plot.png", p)
```

```{r}
# Reset the option
options(ggsaveR.formats = NULL)
```

## Preventing File Overwrites

During a long analysis, you might accidentally overwrite a critical plot. `ggsaveR` provides the `ggsaveR.overwrite_action` option to control this behavior.

The default is `"overwrite"`, which mimics the standard `ggplot2::ggsave` behavior.

### Stop on Existing File

Set the option to `"stop"` to throw an error if the file already exists. This is useful for preventing accidental overwrites in critical scripts.

```{r, eval = FALSE}
options(ggsaveR.overwrite_action = "stop")

# This will work the first time
ggsave("critical_plot.png", p)

# If you run it again, it will throw an error
# ggsave("critical_plot.png", p)
# Error: File 'critical_plot.png' already exists and ggsaveR.overwrite_action is set to 'stop'.
```

### Create a Unique Filename

Alternatively, you can set the option to `"unique"` to automatically generate a new filename if the intended one already exists. This is useful for iterative analyses where you want to keep all versions of a plot.

```{r, eval = FALSE}
options(ggsaveR.overwrite_action = "unique")

# Run this once: creates "versioned_plot.png"
ggsave("versioned_plot.png", p)

# Run this again: creates "versioned_plot-1.png"
ggsave("versioned_plot.png", p)

# And again: creates "versioned_plot-2.png"
ggsave("versioned_plot.png", p)
```

```{r}
# Reset to default
options(ggsaveR.overwrite_action = "overwrite")
```

These intermediate features provide a much finer level of control over how your plots are saved, helping to streamline your workflow and protect your work.
